### 2021-02-26 text/draft.tex
analysis f1 et al

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st (data field
\texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\)) century as
compared to the raw Edoc data. The data foundation is available at
\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
be calculated by calling \texttt{\_Analysis.get\_chi\_square\_fit} on
the data foundation files.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_abc.pdf}
\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
distribution of keywords is strongly skewed right
(\(min = Q1 = M = Q3 = 1\), \(max = 910\)). However, even though
keywords with only one occurrence constitute over 75\% of the total
keywords, their occurrences constitute less than 35\% of the total
occurrences. The most common keywords with 50 or more occurrences are
extreme outliers but make up almost 20\% of the total occurrences.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/keywords_counted.pdf}
\caption{The distribution of keywords per item in the Edoc sample data
set. The leftmost boxplot shows the distribution of cleaned keywords
(\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\), \(max = 87\)); the
other boxplots show the distribution of cleaned keywords with reconciled
QID (\(min = 0\), \(Q1 = 2\), \(M = 4\), \(Q3 = 6\), \(max = 80\)), MeSH
ID (\(min = Q1 = 0\), \(M = 2\), \(Q3 = 4\), \(max = 63\)), and YSO ID
(\(min = Q1 = 0\), \(M = 1\), \(Q3 = 2\), \(max = 46\)). All four
distributions are equally consistent, but there is a linear shrinkage of
the center leaving MeSH and YSO with potentially too few descriptors to
represent an adequate indexing.}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st century
(data field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493,
\(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
available at \texttt{/edoc/analysis/chi\_square...} and the
\(\chi^2\)-statistic can be calculated by calling
\texttt{\_Analysis.get\_chi\_square\_fit} on the data foundation files.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_abc.pdf}
\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
distribution of keywords is strongly skewed right (min = Q1 = M = Q3 =
1, max = 910). However, even though keywords with only one occurrence
constitute over 75\% of the total keywords, their occurrences constitute
less than 35\% of the total occurrences. The most common keywords with
50 or more occurrences are extreme outliers but make up almost 20\% of
the total occurrences.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/keywords_counted.pdf}
\caption{The distribution of keywords per item in the Edoc sample data
set. The leftmost boxplot shows the distribution of cleaned keywords
(min = 0, Q1 = 4, M = 6, Q3 = 8, max = 87); the other boxplots show the
distribution of cleaned keywords with reconciled QID (min = 0, Q1 = 2, M
= 4, Q3 = 6, max = 80), MeSH ID (min = Q1 = 0, M = 2, Q3 = 4, max = 63),
and YSO ID respectively (min = Q1 = 0, M = 1, Q3 = 2, max = 46). All
four distributions are similarly consistent, but there is a linear
shrinkage of the center leaving MeSH and YSO with potentially too few
descriptors to represent an adequate indexing.}
\end{figure}

@@

The metric of F1-score is implemented by \texttt{\_Analysis\_get\_f1}
